---
title: "2022-TINRO-Bongo"
author: "Tim van der Stap"
date: "2022-09-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
library(tidyverse)
library(lubridate)
library(worrms)
library(dplyr)
library(obistools)
library(readxl)
library(parsedate)
library(googledrive)
library(here)
```

## Read in files:

``` {r read_file, warning = FALSE}
tinro2022_bongo_metadata <- read_excel(here("original_data", "7-14 2022 Bongo Logbook-TINRO_clean.xlsx"), sheet = "Bongo metadata")
tinro2022_bongo_data <- read_excel(here("original_data", "7-14 2022 Bongo Logbook-TINRO_clean.xlsx"), sheet = "zoop counts")
```

Create Event Core:

``` {r event core, eval = FALSE}
tinro2022_bongo_event <- tinro2022_bongo_metadata %>%
  select(-`T, surf`) %>%
  mutate(Time = format(`Time, UTC`, "%H:%M:%S"),
         eventDate = format_iso_8601(as.POSIXct(paste(Date, Time),
                                                format = "%Y-%m-%d %H:%M:%S",
                                                tz = "UTC")),
         eventDate = str_replace(eventDate, "\\+00:00", "Z"))

tinro2022_bongo_event$year <- as.numeric(format(as.Date(tinro2022_bongo_event$eventDate), "%Y"))
tinro2022_bongo_event$month <- as.numeric(format(as.Date(tinro2022_bongo_event$eventDate), "%m"))
tinro2022_bongo_event$day <- as.numeric(format(as.Date(tinro2022_bongo_event$eventDate), "%d"))

tinro2022_bongo_event <- tinro2022_bongo_event %>%
  mutate(zone = 3,
         eventID = paste("IYS2022", "TINRO", zone, Station, Gear, `Net number`, sep = "-"),
         minimumDepthInMeters = 0,
         geodeticDatum = "WGS84",
         samplingEffort = "vertical paired bongo tows",
         sampleSizeUnit = "cubic meters")

tinro2022_bongo_event_fnl <- tinro2022_bongo_event %>% 
  select(eventID,
         eventDate,
         year,
         month,
         day,
         decimalLatitude = Latitude,
         decimalLongitude = Longitude,
         minimumDepthInMeters,
         maximumDepthInMeters = `Wire out_m`,
         sampleSizeValue = `Vol filtered (m^3)`,
         eventRemarks = Notes,
         samplingEffort,
         sampleSizeUnit,
         geodeticDatum)

tinro2022_bongo_event <- tinro2022_bongo_event %>%
  mutate(footprintWKT = paste("POINT", " (", tinro2022_bongo_event$decimalLongitude, " ", tinro2022_bongo_event$decimalLatitude, ")"))

coordinates <- obistools::calculate_centroid(tinro2022_bongo_event$footprintWKT) %>% select(coordinateUncertaintyInMeters)

tinro2022_bongo_event <- cbind(tinro2022_bongo_event, coordinates)

# Remove NAs from the dataframe:
tinro2022_bongo_event[is.na(tinro2022_bongo_event)] <- ""
tinro2022_bongo_event <- as.data.frame(tinro2022_bongo_event)

# Save as .csv file
write_csv(tinro2022_bongo_event, here("standardized_data", "tinro2022_bongo_event.csv"))
```

Next, create the occurrence extension:

```{r occurrence extension, eval = FALSE}

tinro2022_bongo_occ <- tinro2022_bongo_data[-c(1:4, 149:151),]

tinro2022_bongo_occ <- tinro2022_bongo_occ %>%
  pivot_longer(cols = `1`:`32`,
               values_to = "ind/m3",
               names_to = "station") 

tinro2022_bongo_occ$station <- as.numeric(tinro2022_bongo_occ$station)
tinro2022_bongo_occ <- tinro2022_bongo_occ[order(tinro2022_bongo_occ$station),]

# Parse out `Stage/length` column into two separate columns:
tinro2022_bongo_occ <- tinro2022_bongo_occ %>%
  mutate(size_range = ifelse(grepl("\\d+", `Stage/length`), `Stage/length`, NA), # if numerics are included, this needs to be included in a separate column (size_range)
         `Stage/length` = ifelse(grepl("\\d+", `Stage/length`), NA, `Stage/length`), # Remove any size ranges from the `Stage/length` column
         sex = ifelse(grepl("F", `Stage/length`), "female", # If `Stage/length` includes an 'F' (i.e. AF), this implies female
                      ifelse(grepl("M", `Stage/length`), "male", NA)), # If `Stage/length` includes an 'M' (i.e. AM) this implies male
         `Stage/length` = ifelse(grepl("A", `Stage/length`), "Adult", `Stage/length`)) %>% # any `Stage/lengths` that include 'A' have to be changed to Adult.
  rename(lifeStage = `Stage/length`,
         verbatimIdentification = `Station No`) %>%
  mutate(eventID = paste("IYS2022", "TINRO", "3", station, "Bongo", "1", sep = "-"))

# Size (ranges) in the verbatimIdentification should also be included in the size_range column
tinro2022_bongo_occ <- tinro2022_bongo_occ %>%
  mutate(size_range = ifelse(grepl("0.5mm", verbatimIdentification), "0.5mm", size_range),
         size_range = ifelse(grepl("1.5mm", verbatimIdentification), "1.5mm", size_range),
         size_range = ifelse(grepl("2.5mm", verbatimIdentification), "2.5mm", size_range),
         size_range = ifelse(grepl("1mm", verbatimIdentification), "1mm", size_range))

# Lifestages in the verbatimidentification should also be included in the lifeStage column:
tinro2022_bongo_occ <- tinro2022_bongo_occ %>%
  mutate(lifeStage = ifelse(grepl("larvae", verbatimIdentification), "larvae", lifeStage),
         lifeStage = ifelse(grepl("juv.", verbatimIdentification), "juvenile", lifeStage),
         lifeStage = ifelse(grepl("egg", verbatimIdentification), "egg", lifeStage))

# Create column 'identificationQualifier' to indicate uncertainty in species classification:
tinro2022_bongo_occ$identificationQualifier <- ifelse(grepl("\\b sp.|spp.", tinro2022_bongo_occ$verbatimIdentification), "sp. indet.", NA)

# Next, duplicate the verbatimIdentification column so that we can make changes where necessary to the scientific names based on the WoRMS Registry:
tinro2022_bongo_occ$scientific_name <- tinro2022_bongo_occ$verbatimIdentification

# From this column, remove 'sp.' and 'spp.' to begin with;
tinro2022_bongo_occ$scientific_name <- gsub("\\b sp.\\b|spp.", "", tinro2022_bongo_occ$scientific_name) 

# Remove any special characters (punctuation, brackets etc)
tinro2022_bongo_occ$scientific_name <- gsub("[[:punct:]]", "", tinro2022_bongo_occ$scientific_name)

# Check accuracy of scientific names:
worms_id <- worrms::wm_records_names(unique(tinro2022_bongo_occ$scientific_name), marine_only = FALSE) %>% dplyr::bind_rows() %>% rename(scientific_name = scientificname)

# Find out which species are not found in the WoRMS database:
no_worms_id <- left_join(tinro2022_bongo_occ, worms_id, by = "scientific_name") %>% filter(is.na(AphiaID)) %>% distinct(scientific_name)

#TODO: 34 names have to be changed to match WoRMS accepted names. These have to be changed in the original data table (tinro2022_bongo_occ)
tinro2022_bongo_occ$scientific_name <- gsub("Scolethricella minor", "Scolecithricella minor", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Scolethricella ovata", "Scolecithricella ovata", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Neocalanus plumchrusflemmingi", "Neocalanus", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Eucheata elongata", "Euchaeta elongata", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Candacia columbia", "Candacia columbiae", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Clausocalanus sp  really small 05mm  tiny 5th leg AF voucher", "Clausocalanus", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Clausocalanus sp  15mm  tiny 5th leg AF voucher", "Clausocalanus", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Clausocalanus sp 1mm", "Clausocalanus", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Clausocalanus sp 25mm", "Clausocalanus", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Mesocalanus tenniucornus", "Mesocalanus tenuicornis", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Acartia longirmis", "Acartia longiremis", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Lucicutia 15mm", "Lucicutia", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Hyperia juv", "Hyperia", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Thysanoesa inspinata", "Thysanoessa inspinata", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Thysanoesa spinifer", "Thysanoessa spinifera", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Thysanoesa inermis", "Thysanoessa inermis", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Thysanoesa longipes", "Thysanoessa longipes", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Chionocetes", "Chionoecetes", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Crytoniscid parasitic isopod larvae", " ", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Microniscid parasitic isopod larvae", " ", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Polycheata", "Polychaeta", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Tyroscrolex leafy stick", " ", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Limiacina helicina", "Limacina helicina", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Squid larvae", "Teuthida", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Eukronia hamata", "Eukrohnia hamata", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Sagitta scrippae  larger transparent fellow", "Sagitta scrippsae", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Oikopluera", "Oikopleura", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Fritilaria", "Fritillaria", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Siphonophore bract", "Siphonophora", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Jelly fragments", " ", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Fish egg", "Pisces", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Fish larvae", "Pisces", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Brozoan cyphonautes", " ", tinro2022_bongo_occ$scientific_name)
tinro2022_bongo_occ$scientific_name <- gsub("Pumkin boy unknown critter could be sea anemone larvae", " ", tinro2022_bongo_occ$scientific_name)

# As we have now changed all the names in the original dataframe to fit the entries in the WoRMS database registry, we can use wm_records_names() again to find all the taxonomic information. 
tinro2022_bongo_worms_id <- worrms::wm_records_names(unique(tinro2022_bongo_occ$scientific_name), marine_only = FALSE) %>%
  dplyr::bind_rows() %>% rename(scientific_name = scientificname)

# After manual inspection, there are some AphiaIDs that need to be removed, as the species is listed multiple times.
tinro2022_bongo_worms_id <- filter(tinro2022_bongo_worms_id, !(AphiaID %in% c("534090", "254409", "503291")))

# Check to see if we missed any:
unique_taxa <- as.data.frame(unique(tinro2022_bongo_occ$scientific_name))
names(unique_taxa)[1] <- "scientificname"
temp_taxa <- left_join(unique_taxa, tinro2022_bongo_worms_id) %>% filter(is.na(AphiaID)) # should be empty.
print(temp_taxa)

#TODO: Find a solution for species that no WoRMS LSID can be found for: 'Crytoniscid parasitic isopod larvae', 'Microniscid parasitic isopod larvae', 'Tyroscrolex leafy stick', 'Jelly fragments' and 'Brozoan cyphonautes' and 'Pumkin boy unknown critter could be sea anemone larvae'. 

tinro2022_bongo_occ <- left_join(tinro2022_bongo_occ, tinro2022_bongo_worms_id, by = "scientific_name") %>%
  group_by(eventID) %>%
  mutate(id = seq_along(eventID)) %>%
  mutate(occurrenceID = paste(eventID, id, sep = "-"),
         occurrenceStatus = "present",
         preparations = "Formalin")

tinro2022_bongo_final <- tinro2022_bongo_occ %>%
  select(verbatimIdentification, lifeStage, sex, eventID, identificationQualifier, 
         scientificName = scientific_name,
         taxonomicAuthority = authority,
         taxonomicStatus = status,
         taxonomicRank = rank,
         kingdom, phylum, class, order, family, genus, 
         scientificNameID = lsid,
         occurrenceID, occurrenceStatus, preparations) %>%
  mutate(specificEpithet = stringr::word(scientificName, 2))

# Remove NAs from the dataframe:
tinro2022_bongo_final[is.na(tinro2022_bongo_final)] <- ""
tinro2022_bongo_final <- as.data.frame(tinro2022_bongo_final)

# Save as .csv file
write_csv(tinro2022_bongo_final, here("standardized_data", "tinro2022_bongo_occ.csv"))
```

Finally, develop the extended measurements or facts extensions and combine them.

Bottom depth:

```{r bottom_depth, eval = FALSE}
bongo2022_bottomdepth <- tinro2022_bongo_event %>%
  select(eventID,
         Depth_m) %>%
  distinct(eventID, .keep_all = TRUE) %>%
  mutate_all(as.character) %>%
  pivot_longer(cols = Depth_m,
               names_to = "measurementType",
               values_to = "measurementValue") %>%
  mutate(
    measurementType = recode(measurementType,
                                 Depth_m = "bottom_depth"),
    measurementID = paste(eventID, measurementType, sep = "-")) %>%
  mutate(measurementTypeID = case_when(
    measurementType == "bottom_depth" ~ "http://vocab.nerc.ac.uk/collection/C00/current/SCILOG/"),
        measurementUnit = case_when(
    measurementType == "bottom_depth" ~ "meter"),
        measurementUnitID = case_when(
    measurementUnit == "meter" ~ "http://vocab.nerc.ac.uk/collection/P06/current/ULAA/"),
    measurementValueID = NA) %>%
  select(eventID, measurementID, measurementType, measurementTypeID, measurementValue, measurementValueID,
         measurementUnit, measurementUnitID)
```

Sampling effort:

``` {r sampling effort, eval = FALSE}
bongo2022_sampling <- tinro2022_bongo_event %>%
  select(eventID, 
         `Vol filtered (m^3)`) %>%
  mutate(speed_tow = 1) %>%
  distinct(eventID, .keep_all = TRUE) %>%
  mutate_all(as.character) %>%
  pivot_longer(cols = `Vol filtered (m^3)`:speed_tow,
               names_to = "measurementType",
               values_to = "measurementValue") %>%
  mutate(measurementType = recode(measurementType,
                                 `Vol filtered (m^3)` = "volume_filtered"),
         measurementID = paste(eventID, measurementType, sep = "-"),
         measurementTypeID = case_when(
           measurementType == "volume_filtered" ~ "http://vocab.nerc.ac.uk/collection/P09/current/VOLF/", 
           measurementType == "speed_tow" ~ "http://vocab.nerc.ac.uk/collection/P01/current/TOWSPEED/"),
  measurementUnit = case_when(
    measurementType == "volume_filtered" ~ "cubic meter",
    measurementType == "speed_tow" ~ "meter per second"),
  measurementUnitID = case_when(
    measurementUnit == "cubic meter" ~ "http://vocab.nerc.ac.uk/collection/P06/current/MCUB/",
    measurementUnit == "meter per second" ~ "http://vocab.nerc.ac.uk/collection/P06/current/UVAA/"),
  measurementValueID = NA) %>%
    select(eventID, measurementID, measurementType, measurementTypeID, measurementValue, measurementValueID,
           measurementUnit, measurementUnitID)
```

Next, add information on the _sampling instrument_. Information on the mesh size and sampling instrument opening came from the Cruise Report and is verified by the data provider. 

``` {r samplingInstrument, eval = FALSE}
bongo2022_instrument <- tinro2022_bongo_event %>%
  select(eventID,
         Gear) %>%
  mutate(bongo_mesh = 236,
         bongo_opening = 0.6) %>%
  distinct(eventID, .keep_all = TRUE) %>%
  mutate_all(as.character) %>%
  pivot_longer(cols = Gear:bongo_opening,
               names_to = "measurementType",
               values_to = "measurementValue") %>%
  mutate(measurementID = paste(eventID, "bongo", measurementType, sep = ":"),
         measurementTypeID = case_when(
           measurementType == "Gear" ~ "http://vocab.nerc.ac.uk/collection/Q01/current/Q0100002/",
           measurementType == "bongo_mesh" ~ "http://vocab.nerc.ac.uk/collection/Q01/current/Q0100015/",
           measurementType == "bongo_opening" ~ "http://vocab.nerc.ac.uk/collection/Q01/current/Q0100017/"))

bongo2022_instrument <- bongo2022_instrument %>%
  mutate(measurementUnit = case_when(
           measurementType == "bongo_mesh" ~ "micrometer",
           measurementType == "bongo_opening" ~ "square meter"),
         measurementUnitID = case_when(
           measurementUnit == "micrometer" ~ "http://vocab.nerc.ac.uk/collection/P06/current/UMIC/",
           measurementUnit == "square meter" ~ "http://vocab.nerc.ac.uk/collection/P06/current/UMSQ/"),
         measurementValueID = case_when(
           measurementValue == "Bongo" ~ "http://vocab.nerc.ac.uk/collection/L22/current/NETT0176/")) %>%
  select(eventID, measurementID, measurementType, measurementTypeID, measurementValue,
         measurementValueID, measurementUnit, measurementUnitID)
```

Next, we create the eMOF extension to associate the length, lifestage and sex measurements to the zooplankton.  

```{r eMOF, eval = FALSE}
bongo2022_emof <- tinro2022_bongo_occ %>%
  select(eventID,
         occurrenceID,
         lifeStage,
         sex,
         `ind/m3`, 
         size_range) %>%
  mutate_all(as.character)
```

```{r specimen size range, eval = FALSE}
#TODO: Create code to parse out size ranges into separate columns

range <- dplyr::filter(bongo2022_emof, grepl("-", size_range)) %>%
  separate(col = size_range, into = c("minimumLength", "maximumLength"), sep = "\\-") %>%
  mutate(size_range = " ")

# Remove any rows where length_mm contains a range, add two dummy columns (minimumLength and maximumLength) and use rbind() to merge `range` with this newly created dataframe.
minimum <- dplyr::filter(bongo2022_emof, grepl("\\+|>", size_range)) %>%
  mutate(minimumLength = as.character(unlist(regmatches(size_range, 
                                                      gregexpr("[[:digit:]]+\\.*[[:digit:]]*", size_range)))),
         maximumLength = " ")

temp <- bongo2022_emof[ -grep("\\+|>|-", bongo2022_emof$size_range), ] %>%
  mutate(minimumLength = " ",
         maximumLength = " ")

bongo2022_emof_fnl <- rbind(range, minimum, temp)

# Remove 'mm' from the size (range) columns:
bongo2022_emof_fnl[c("minimumLength", "maximumLength", "size_range")] <- lapply(bongo2022_emof_fnl[c("minimumLength", "maximumLength", "size_range")], function(y) gsub("mm", "", y))

# Make some adjustments:
bongo2022_emof_fnl$length_type <- ifelse(grepl("shell", bongo2022_emof_fnl$maximumLength), "shell length", NA)
bongo2022_emof_fnl$maximumLength <- gsub("[[:punct:]]", "", bongo2022_emof_fnl$maximumLength)
bongo2022_emof_fnl$maximumLength <- gsub(" shell length", "", bongo2022_emof_fnl$maximumLength)

#Rremove 'fur' from minimumLength and add it to lifeStage column (assuming fur = fucilia)
bongo2022_emof_fnl$lifeStage <- ifelse(grepl("fur", bongo2022_emof_fnl$minimumLength), "furcilia", bongo2022_emof_fnl$lifeStage)
bongo2022_emof_fnl$minimumLength <- gsub("fur", "", bongo2022_emof_fnl$minimumLength)

# Remove 'lar' from size_range and add it to lifeStage column (assuming lar = larvae)
bongo2022_emof_fnl$lifeStage <- ifelse(grepl("lar", bongo2022_emof_fnl$size_range), "larvae", bongo2022_emof_fnl$lifeStage)
bongo2022_emof_fnl$size_range <- gsub("lar", "", bongo2022_emof_fnl$size_range)

#TODO: Figure out what to do with 'Megalopa' in the Stage/Length column:

#Extract only sizes (numerical values) from size_range, remove all characters.
bongo2022_emof_fnl$size_range <- extract_numeric(bongo2022_emof_fnl$size_range)
```

So then finally the eMOF:

```{r emof cont., eval = FALSE}

bongo2022_emof_fnl <- bongo2022_emof_fnl %>%
  mutate_all(as.character) %>%
  pivot_longer(cols = lifeStage:length_type,
               names_to = "measurementType",
               values_to = "measurementValue") %>%
  mutate(measurementID = paste(occurrenceID, measurementType, sep = "-"),
    measurementTypeID = case_when(
      measurementType == "size_range" ~ "http://vocab.nerc.ac.uk/collection/P01/current/OBSINDLX/",
      measurementType == "maximumLength" ~ "http://vocab.nerc.ac.uk/collection/P01/current/OBSMAXLX/",
      measurementType == "minimumLength" ~ "http://vocab.nerc.ac.uk/collection/P01/current/OBSMINLX/",
      measurementType == "lifeStage" ~ "http://vocab.nerc.ac.uk/collection/P01/current/LSTAGE01/",
      measurementType == "sex" ~ "http://vocab.nerc.ac.uk/collection/P01/current/ENTSEX01/",
      measurementType == "ind/m3" ~ "http://vocab.nerc.ac.uk/collection/P01/current/SDBIOL01/",
      measurementType == "length_type" ~ " "), 
    measurementUnit = case_when(
      measurementType %in% c("length", "minimumLength", "maximumLength") ~ "millimeter",
      measurementType == "ind/m3" ~ "individuals per cubic meter"), 
    measurementUnitID = case_when(
      measurementUnit == "millimeter" ~ "http://vocab.nerc.ac.uk/collection/P06/current/UXMM/",
      measurementUnit == "individuals per cubic meter" ~ "http://vocab.nerc.ac.uk/collection/P06/current/UPMM/"),
    measurementValueID = case_when(
      measurementValue == "male" ~ "http://vocab.nerc.ac.uk/collection/S10/current/S103/",
      measurementValue == "female" ~ "http://vocab.nerc.ac.uk/collection/S10/current/S102/",
      measurementValue == "Adult" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1116/",
      measurementValue == "V" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1112/",
      measurementValue == "IV" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1110/",
      measurementValue == "IV-V" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1111/",
      measurementValue == "III" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S118/",
      measurementValue == "II" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S117/",
      measurementValue == "I" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S111/",
      measurementValue == "juvenile" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1127/",
      measurementValue == "furcilia" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1123/",
      measurementValue == "egg" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1122/",
      measurementValue == "nauplii" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1130/",
      measurementValue == "cal" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1118/",
      measurementValue == "larvae" ~ "http://vocab.nerc.ac.uk/collection/S11/current/S1128/"),
    measurementRemarks = NA) %>%
  drop_na(measurementValue)

bongo2022_tinro_emof <- bind_rows(bongo2022_bottomdepth, bongo2022_sampling, bongo2022_instrument, bongo2022_emof_fnl)

# Make sure the folder path exists already (e.g. ./Bongo/tidy_data)
write_csv(bongo2022_tinro_emof, here("standardized_data", "bongo2022_tinro_emof.csv"))
```












